Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2018-11-21 papers/paper/paper.tex

%% \begin{figure}[tbhp]
%%   \centering
%% \includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
%% \includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
%% \includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
%% \includegraphics[width=0.5\columnwidth]{figures/schematic-full}
%%   \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
%%       images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
%%     dynein heavy chains superimposed with model motor angles, both
%%     from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
%%     MT with model binding angle superimposed, from
%%     \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
%%     bound to an MT with model superimposed, from
%%     \textbf{nativestructure}.}
%% \label{fig:modelangles}
%% \end{figure}

>>>>

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=0.5\columnwidth]{figures/model-cartoon-simple}%
  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_angles_bd.pdf}\\
  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_taily_positions}%
  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\\
  \includegraphics[width=0.5\columnwidth]{../../plots/onebound_stroke_tailx_positions}%
  \includegraphics[width=0.5\columnwidth]{../../plots/bothbound_stroke_angles_md}\\
  \caption{\textbf{Model behavior during power stroke.}}
\label{fig:stroke}
\end{figure}
